\plaintitle

### 2016-07-16 drafts/labor/introduction.tex
reorg to be less hopeful :P

\documentclass[trackingWork]{subfiles}
\makeatletter
\def\blx@maxline{77}
\makeatother
\begin{document}
\section{Introduction}
\onlyinsubfile{}
% what would a cynical reader make bullet points out of?
% each sentence feels like a thought that's unrelated to the next one
The past decade has seen a proliferation of transient labor.
% beginning with ``information work'' such as on
% Amazon Mechanical Turk (AMT).
% ??? ->
Stemming from the recognition that
complex tasks might be achievable
--- and indeed trivial ---
through the effective management of the ``crowd'',
researchers have rapidly begun exploring
the space for opportunities to facilitate new (and revisit familiar) forms of work
\cite{bernsteinSoylent,redballoon}.
%  ??? -->
Broadly, this work has imagined the various applications of ``gig''--based work,
and making it work for ``requesters''
--- academics, industries, and to some extent end--users
who might benefit from the product of crowd--powered work
\cite{hong2015group,jonBrelig,paolacci2010running}.
% ??? -->
Since then,
the application of digitally mediated environments acting as rapid ``hiring halls''
for on--demand tasks
has found purchase far beyond the context of ``information work'' like Amazon Mechanical Turk (AMT);
livery services (Uber), cleaning (Handy), and various other services (TaskRabbit)
% parentheticals giving examples?
have garnered the interest of both industry and research.

>>>>

% %!TEX root = ./trackingWork.tex
\documentclass[trackingWork]{subfiles}
\makeatletter
\def\blx@maxline{77}
\makeatother
\begin{document}
\section{Introduction}
% each sentence feels like a thought that's unrelated to the next one
The past decade has seen a proliferation in on--demand work
where workers' statuses are so fleeting that
they have been described as ``transient''.
After identifying that myriad tasks
--- from the mundane to the complex ---
can be accomplished
% beginning with ``information work'' such as on
% Amazon Mechanical Turk (AMT).
% ??? ->
% Stemming from the recognition that
% complex tasks might be achievable
% --- and indeed trivial ---
by directing and managing the ``crowd'',
the research and and industry communities have flocked to sites of labor
like Amazon's Mechanical Turk (AMT)
to solicit workers.
Researchers in particular have taken to the space in earnest,
finding opportunities to enable new forms of work
as well as using these workers (``Turkers'')
as representative populations of the public
\cite{bernsteinSoylent,redballoon,paolacci2010running}.

This approach to managing work (and in particular workers)
can be differentiated from other formulations by a constellation of traits:
\begin{inlinelist}
\item distributing the workforce,
\item distancing workers from the context of the work, and
\item compensating work on a per--task basis rather than for time
\end{inlinelist}.
These features can be found elsewhere
--- for instance,
distributed workforces
are a well--known feature of a global economy,
%
and abstracting workers from the products of their labor
is well--associated with
\citeauthor{marx2012economic} ---
but these individual components have been explored to some extent
(for instance, \citeauthor{fevre1986contract} and later \citeauthor{kalleberg2000nonstandard}),
and we focus on the newfound interest in
this particular paradigm of work
% While contract work is familiar enough,
% much of this work focuses on comprehensive work
% (for example, creative or professional work like landscaping, design, etc\dots)
\cite{kalleberg2000nonstandard,fevre1986contract,marx2012economic}.

On--demand work under this formulation
has sparked interest across industries ranging from
livery (driving for hire, for example Uber),
house--cleaning (Handy),
and various other services (TaskRabbit)
\cite{uberOfficial,zaarlyOfficial,taskrabbitOfficial}.
Today, a rapidly growing transient workforce is forming,
itself assembling piece--by--piece as industries and researchers find more and more unexpected ways
to benefit from a latent pool of variably skilled workers.

Broadly, this work has imagined the various applications of ``gig''--based work,
and making it work for ``requesters''
--- academics, industries, and to some extent end--users
who might benefit from the product of crowd--powered work
\cite{hong2015group,jonBrelig,paolacci2010running}.
% ??? -->
Since then,
the application of digitally mediated environments acting as rapid ``hiring halls''
for on--demand tasks
has found purchase far beyond the context of ``information work'' like Amazon Mechanical Turk (AMT);
livery services (Uber), cleaning (Handy), and various other services (TaskRabbit)
% parentheticals giving examples?
have garnered the interest of both industry and research.
